FocalGstar

### 2017-06-16 analysis.Rmd
all legends moved to topleft

lines(y1, col = "blue", lw = 2)
lines(y2, col = "red", lw = 2)
legend(1,1, c("G*", "Focal G*"), fill = c("blue", "red"))
```

@@

lines(y1, col = "blue", lw = 2)
lines(y2, col = "red", lw = 2)
legend(7,1, c("G*", "Focal G*"), fill = c("blue", "red"))
```

>>>>

lines(y1, col = "blue", lw = 2)
lines(y2, col = "red", lw = 2)
legend("topleft", c("G*", "Focal G*"), fill = c("blue", "red"))
```

@@

lines(y1, col = "blue", lw = 2)
lines(y2, col = "red", lw = 2)
legend("topleft", c("G*", "Focal G*"), fill = c("blue", "red"))
```
